First of all, I would like to thank my supervisors Prof. Dr. Florentin W\"org\"otter and Prof. Dr. Wolfgang May for guiding me through my work by sharing their experiences with me and for countless hours of fruitful discussions without which this work would not have been successful. 
This work has been done in collaboration with Dr. Eren Erdal Aksoy, Dr. Jan-Matthias Braun, Dr. Alejandro Agostini, and Prof. Dr. Babette Dellen, so I am very thankful for their efforts, too.

Second, I would like to thank all my colleagues and friends for their direct and/ or indirect input to my work and for having great time together. 
Many thanks go to Aisha Aamir, Dr. Alexey Abramov, Dr. Mohamad Javad Aein, Johannes Auth, Moritz Becker, Dr. Sakyasingha Dasgupta, Dr. Michael Fauth, Dennis Goldschmidt, Juliane Herpich, Sebastian Herzog, Dr. Tatyana Ivanovska, Dr. David Kappel, Prof. Dr. Tomas Kulvicius, Jannik Luboeinski, Timo Lüddecke, Prof. Dr. Poramate Manoonpong, Dr. Daniel Miner, Dr. Timo Nachstedt, Dr. Jeremie Papon, Dr. Mayte Bonilla Quintana, Dr. Jan Markus Schoeler, Mina Lilly Shibata, Prof. Dr. Minija Tamosiunaite, Florian Teich, Dr. Christian Tetzlaff, Dr. Xiaofeng Xiong, Erenus Yildiz, and Fatemeh Ziaeetabar.
An especially big thanks to Ursula Hahn-W\"org\"otter who was always a big help.
Next, I would like to thank all members of the Feinmechanikwerkstatt and Elektronikwerkstatt of the Third Insitute of Physics.
Without their detailed knowledge, patience, and outstanding craftsmanship many projects would not have been possible.
A big thanks to all other members of the Third Insitute of Physics for your support and help.

Third, I would like to thank all my Bachelor and Master students: Dami\-an Bast, Lars Berscheid, Caroline Campbell, Philipp D\"onges, Martin Hei\-ne\-mann, Georg Jahn, Johann Kalies, Daniel Kalin, Erik Schultheis, Maurice Seer, and Kevin Vorwerk.
It was always a big pleasure working with you.

A special thanks goes to my parents without whom I would not have achieved all that in my life what I have now. 
Thank you all for the patience, understanding, support and being always by my side no matter what.

Thank you very much indeed!
\vspace{1cm}\\
Simon Reich\\G\"ottingen, 2018.
